Funding programmes for early career researchers marginally improves their collaboration independence, but not cognitive independence

### 2023-10-05 _targets.Rmd
errors in data repaired (in match_data prep and read_one_author) + article updated + changes in the data infrastructure (instead of sup_control and sup_control_second now fused into one file "all_sup" and additional file "blacklist_control"

  tarchetypes::tar_download(ids_path,
      urls = Sys.getenv("link_to_supervisors"),
      paths = here::here("data", "raw", "supervisors.csv")),
  tarchetypes::tar_download(gender_path,
      urls = Sys.getenv("link_to_gender"),
      paths = here::here("data", "raw", "names4api_tagged.tsv")),
  tarchetypes::tar_download(authors_arrow_path,
      urls = Sys.getenv("link_to_updated_authors"),
      paths = here::here("data", "raw", "authors_by_pubs.arrow"),
       mode = "wb"),
  tarchetypes::tar_download(text_arrow_path,
      urls = Sys.getenv("link_to_updated_texts"),
      paths = here::here("data", "raw", "riv_text.arrow"),
      mode = "wb"),
  tarchetypes::tar_download(cep_investigators_path,
      urls = Sys.getenv("link_to_cep_investigators"),
      paths = here::here("data", "raw", "cep_investigators.arrow"),
       mode = "wb"),
  tarchetypes::tar_download(cep_details_path,
      urls = Sys.getenv("link_to_cep_details"),
      paths = here::here("data", "raw", "cep_details.arrow"),
       mode = "wb"),
  tarchetypes::tar_download(riv_details_path,
      urls = Sys.getenv("link_to_riv_details"),
      paths = here::here("data", "raw", "riv_details.arrow"),
       mode = "wb"),
  tarchetypes::tar_download(riv_authors_path,
      urls = Sys.getenv("link_to_riv_authors"),
      paths = here::here("data", "raw", "riv_authors.arrow"),
       mode = "wb"),
   tarchetypes::tar_download(sup_path,
      urls = Sys.getenv("link_to_manual_sup_search"),
      paths = here::here("data", "raw", "manual_sup_search.csv")),
  tarchetypes::tar_download(sup_path_second,
      urls = Sys.getenv("link_to_manual_sup_search_second"),
      paths = here::here("data", "raw", "manual_sup_search_second.csv")),

     # tar_target(ids_path, here::here("data", "raw", "supervisors_updated.csv"), format = "file"),
     tar_target(ids, read.csv(ids_path)),
     # tar_target(gender_path, here::here("data", "raw", "names4api_tagged.tsv"), format = "file"),
     tar_target(gender, read.delim(gender_path)),
     tar_target(authors_arrow, arrow::read_feather(authors_arrow_path)),
     tar_target(text_arrow, arrow::read_feather(text_arrow_path)),
     tar_target(cep_investigators_arrow, arrow::read_feather(cep_investigators_path)),
     tar_target(cep_details_arrow, arrow::read_feather(cep_details_path)),
     tar_target(riv_details_arrow, arrow::read_feather(riv_details_path)),
     tar_target(riv_authors_arrow, arrow::read_feather(riv_authors_path)),
     tar_target(name = db_path, 
                command = transcribe_database(path = here::here("data",
                                                                "raw",
                                                                "czech_sci_db.sqlite"),
                                              authors_arrow, 
                                              cep_investigators_arrow,   
                                              cep_details_arrow, 
                                              riv_details_arrow, 
                                              riv_authors_arrow,
                                              text_arrow),
                format = "file"
                ),
     tar_target(sup_control, read.csv(sup_path)),
     tar_target(sup_control_second, read.csv(sup_path_second))

@@

      tar_target(matching_data, match_data_prep(db_path, ids, gender, sup_control, sup_control_second)),
      tar_target(matched_obj_unfunded, match_obj_unfunded(matching_data)), 
      tar_target(matched_obj_funded, match_obj_funded(db_path, matching_data)),
      tar_target(matching, match_data(matched_obj_unfunded, matched_obj_funded))

@@

 tar_target(sup_complete, create_sup_complete(sup_control, sup_control_second, db_path, matching_data)),
     tar_target(ids_complete, create_ids_complete(ids, db_path, matching_data)),
      tar_target(final_data, connect_data(matching, db_path, ids_complete, sup_complete)),

@@

>>>>

  tarchetypes::tar_download(ids_path,
      urls = Sys.getenv("link_to_supervisors"),
      paths = here::here("data", "raw", "supervisors.csv")),
  tarchetypes::tar_download(gender_path,
      urls = Sys.getenv("link_to_gender"),
      paths = here::here("data", "raw", "names4api_tagged.tsv")),
  tarchetypes::tar_download(authors_arrow_path,
      urls = Sys.getenv("link_to_updated_authors"),
      paths = here::here("data", "raw", "authors_by_pubs.arrow"),
       mode = "wb"),
  tarchetypes::tar_download(text_arrow_path,
      urls = Sys.getenv("link_to_updated_texts"),
      paths = here::here("data", "raw", "riv_text.arrow"),
      mode = "wb"),
  tarchetypes::tar_download(cep_investigators_path,
      urls = Sys.getenv("link_to_cep_investigators"),
      paths = here::here("data", "raw", "cep_investigators.arrow"),
       mode = "wb"),
  tarchetypes::tar_download(cep_details_path,
      urls = Sys.getenv("link_to_cep_details"),
      paths = here::here("data", "raw", "cep_details.arrow"),
       mode = "wb"),
  tarchetypes::tar_download(riv_details_path,
      urls = Sys.getenv("link_to_riv_details"),
      paths = here::here("data", "raw", "riv_details.arrow"),
       mode = "wb"),
  tarchetypes::tar_download(riv_authors_path,
      urls = Sys.getenv("link_to_riv_authors"),
      paths = here::here("data", "raw", "riv_authors.arrow"),
       mode = "wb"),
   tarchetypes::tar_download(sup_path,
      urls = Sys.getenv("link_to_manual_sup_search"),
      paths = here::here("data", "raw", "manual_sup_search.csv")),
  tarchetypes::tar_download(sup_path_second,
      urls = Sys.getenv("link_to_manual_sup_search_second"),
      paths = here::here("data", "raw", "manual_sup_search_second.csv")),
  tarchetypes::tar_download(blacklist_path,
      urls = Sys.getenv("link_to_blacklist_control"),
      paths = here::here("data", "raw", "blacklist_control_after_disamb.csv")),
  tarchetypes::tar_download(all_sup_path,
      urls = Sys.getenv("link_to_all_sup"),
      paths = here::here("data", "raw", "all_sup.csv")),

     # tar_target(ids_path, here::here("data", "raw", "supervisors_updated.csv"), format = "file"),
     tar_target(ids, read.csv(ids_path)),
     # tar_target(gender_path, here::here("data", "raw", "names4api_tagged.tsv"), format = "file"),
     tar_target(gender, read.delim(gender_path)),
     tar_target(authors_arrow, arrow::read_feather(authors_arrow_path)),
     tar_target(text_arrow, arrow::read_feather(text_arrow_path)),
     tar_target(cep_investigators_arrow, arrow::read_feather(cep_investigators_path)),
     tar_target(cep_details_arrow, arrow::read_feather(cep_details_path)),
     tar_target(riv_details_arrow, arrow::read_feather(riv_details_path)),
     tar_target(riv_authors_arrow, arrow::read_feather(riv_authors_path)),
     tar_target(name = db_path, 
                command = transcribe_database(path = here::here("data",
                                                                "raw",
                                                                "czech_sci_db.sqlite"),
                                              authors_arrow, 
                                              cep_investigators_arrow,   
                                              cep_details_arrow, 
                                              riv_details_arrow, 
                                              riv_authors_arrow,
                                              text_arrow),
                format = "file"
                ),
     tar_target(sup_control, read.csv(sup_path)),
     tar_target(sup_control_second, read.csv(sup_path_second)),
     tar_target(blacklist_control, read.csv(blacklist_path)),
     tar_target(all_sup, read.csv(all_sup_path))

@@

      tar_target(matching_data, match_data_prep(db_path, ids, gender, blacklist_control)),
      tar_target(matched_obj_unfunded, match_obj_unfunded(matching_data)), 
      tar_target(matched_obj_funded, match_obj_funded(db_path, matching_data)),
      tar_target(matching, match_data(matched_obj_unfunded, matched_obj_funded))

@@

 tar_target(sup_complete, create_sup_complete(all_sup, db_path, matching_data)),
     tar_target(ids_complete, create_ids_complete(ids, db_path, matching_data)),
      tar_target(final_data, connect_data(matching, db_path, ids_complete, sup_complete)),

@@

# Attachments and additional analyses

Here we test to what extent can PhD advisors be identified algorithmically.

```{r, engine="targets", attachments}

    tar_target(sup_alg,
               refine_data(matching, db_path, sup_complete))

### 2023-10-05 article.Rmd
errors in data repaired (in match_data prep and read_one_author) + article updated + changes in the data infrastructure (instead of sup_control and sup_control_second now fused into one file "all_sup" and additional file "blacklist_control"

---
title: "Funding programmes for early career researchers influence their independence"
author: "David Janků"
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
  word_document: default
always_allow_html: yes
bibliography: merged.bib
csl: apa.csl
---

@@

In the second step, we manually searched for PhD advisors of these 341 researchers in the databases of theses and dissertations that cover most universities in Czechia (https://theses.cz and https://dspace.cuni.cz/). We were able to match `r nrow(tar_read(ids_complete))` researchers with a PhD advisor (69,2 % of the Czech subsample). Further, we have not managed to find a suitable matched pair for another `r nrow(tar_read(ids_complete))-nrow(tar_read("matching") %>% filter(treatment == 1) %>% distinct(vedidk))` researchers in the matching procedure, reducing our final sample to `r nrow(tar_read("matching") %>% filter(treatment == 1) %>% distinct(vedidk))`.

@@

@@

POZN: here we show data

@@

filtered_data_disc_1 <- filtered_by_subclass_1 %>%
  group_by(field) %>%
  filter(n() >= 10)

@@

Importantly, there was a significant interaction effect between treatment and independence_timing on independence, F(`r format(summary(result)$"Error: Within"[[1]]$"Df"[2])`, `r format(summary(result)$"Error: Within"[[1]]$"Df"[3])` = `r format(summary(result)$"Error: Within"[[1]]$"F value"[2], digits=2)`, p = `r format(summary(result)$"Error: Within"[[1]]$"Pr(>F)"[2], digits=2)`. This interaction effect explained about `r format(eta_sq_result[eta_sq_result$Parameter == "treatment:independence_timing", "Eta2_partial"] * 100, digits=2)`% of the variability (partial \(\eta^2 = `r eta_sq_result[eta_sq_result$Parameter == "treatment:independence_timing", "Eta2_partial"]`\), 95% CI [`r eta_sq_result[eta_sq_result$Parameter == "treatment:independence_timing", "CI_low"]`, `r eta_sq_result[eta_sq_result$Parameter == "treatment:independence_timing", "CI_high"]`]).

@@

filtered_data_disc_2 <- filtered_by_subclass_2 %>%
  group_by(field) %>%
  filter(n() >= 10)

@@

@@

The results of this study provide important insights into the effects of funding interventions on researcher independence. The strongest effect we found across all control group comparison was the effect of time - over time, researchers become more independent, regardless of their access to funding or their study discipline. This effect explains around 60% of the variance in independence.

Additionally, the observed variation in independence across different disciplines underscores the importance of considering disciplinary differences, suggested by a moderate effect size. A moderate effect size for the field effect emphasizes that certain disciplines might inherently have variations in RII, perhaps due to differences in practices, methodologies, or norms specific to each discipline. Anyway, these differences remain constant across time and funding interventions, suggesting that funding has a uniform effect on the independence across disciplines.

Finally, the significant interaction between treatment and time when comparing treatment vs unfunded group suggests the funding has positive effect on stimulating researchers' independence. However, the effect size is only modest, explaining about 2 % of variance in independence, indicating relatively small practical relevance. Further, the insignificant interaction when comparing the treatment vs funded control group suggests that funding in this career stage has the same effect, regardless of its type or source. Interestingly, in our sample both funded groups (treatment as well as control) started with lower independence compared to unfunded control group. This might suggest that in the early career stages, in order to secure funding, it is needed to be more dependent on one's PhD advisor.

@@

--> only talks about the Czech environment and considers researchers growing up and most of their careers in the Czech republic

@@

## construction of the independnece identificator

Correlation of its components

correlation with other stuff

- test whether results for the "cognitive" part are the same as results for the "collaboration" part -> do all the tests

@@

Data about PhD student-PhD advisor connections are usually not available. One must search for these connections manually on the internet, which is time consuming and not fully reliable (we were only able to find about 69 % of these connections in our treatment group). Therefore, we tried to come up with an alternative way of identifying supervisors from the available data: we assumed that since many researchers only start their publication career during their PhD studies, their PhD supervisors might often coauthor their first publications. That led us to creating an algorithm to identify the supervisor solely from the student's publication history as "the most frequent co-author of the first 5 publications".

To check whether we can use "the most frequent co-author of the first 5 publications" as a proxy to identify supervisors, we have compared the supervisors identified via this method with the manually found supervisors for each researcher in our sample.
In the treatment group of `r nrow(tar_read(ids_complete))`researchers,  118 (49 %) had their most frequent co-author same as their supervisor and 86 (36 %) had someone other than their supervisor as their most frequent co-author in their first 5 publications, and 37 (15%) had no co-author in their first 5 publications.  
In the control groups, we have manually found supervisors for `r nrow(tar_read(sup_complete) %>% filter(!is.na(sup_vedidk)) %>% distinct(name_first, name_last))` researchers, and when we compared them to the supervisors suggested by the most frequent coauthor algorithm, we found that 41 (29 %) had their most frequent co-author the same as their supervisor, 80 (57 %) had someone other than their supervisor as their most frequent co-author in their first 5 publications, and 20 (14 %) had no co-author in their first 5 publications.

@@

>>>>

---
title: "Funding programmes for early career researchers marginally improves their collaboration independence, but not cognitive independence"
author: "David Janků"
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
  word_document: default
always_allow_html: yes
bibliography: merged.bib
csl: apa.csl
---

@@

In the second step, we manually searched for PhD advisors of these 341 researchers in the databases of theses and dissertations that cover most universities in Czechia (https://theses.cz and https://dspace.cuni.cz/). We were able to match `r nrow(tar_read(ids_complete))` researchers with a PhD advisor (81 % of the Czech subsample). Further, we have not managed to find a suitable matched pair for another `r nrow(tar_read(ids_complete))-nrow(tar_read("matching") %>% filter(treatment == 1) %>% distinct(vedidk))` researchers in the matching procedure, reducing our final sample to `r nrow(tar_read("matching") %>% filter(treatment == 1) %>% distinct(vedidk))`.

@@

To calculate this indicator, we required at least 3 publications. This led to an increased number of missing observations (see section Results -> Descriptives -> Missing data).

@@

@@

filtered_data_disc_1 <- filtered_by_subclass_1 %>%
  group_by(field) %>%
  filter(n() >= 8)

@@

Importantly, there was a significant interaction effect between treatment and independence_timing on independence, F(`r format(summary(result)$"Error: Within"[[1]]$"Df"[2])`, `r format(summary(result)$"Error: Within"[[1]]$"Df"[3])`) = `r format(summary(result)$"Error: Within"[[1]]$"F value"[2], digits=2)`, p = `r format(summary(result)$"Error: Within"[[1]]$"Pr(>F)"[2], digits=2)`. This interaction effect explained about `r format(eta_sq_result[eta_sq_result$Parameter == "treatment:independence_timing", "Eta2_partial"] * 100, digits=2)`% of the variability (partial \(\eta^2 = `r eta_sq_result[eta_sq_result$Parameter == "treatment:independence_timing", "Eta2_partial"]`\), 95% CI [`r eta_sq_result[eta_sq_result$Parameter == "treatment:independence_timing", "CI_low"]`, `r eta_sq_result[eta_sq_result$Parameter == "treatment:independence_timing", "CI_high"]`]).

@@

filtered_data_disc_2 <- filtered_by_subclass_2 %>%
  group_by(field) %>%
  filter(n() >= 8)

@@

## Collaborative vs Cognitive Independence

From the correlation matrix below, we can observe that the cognitive part of independence indicator (ind_topics) has notably lower correlation with the overall indicator (RII) and its remaining parts.

cor_data <- d %>% dplyr::select(RII, ind_topics, ind_pubs, clustr, eig_centr)

cor_matrix <- cor(cor_data, use = "pairwise.complete.obs")

# reversed_cor_matrix <- cor_matrix[rev(rownames(cor_matrix)), rev(colnames(cor_matrix))]

kable(cor_matrix, format = "html", digits = 2) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

ind_top_mean_before <- d %>% 
    filter(independence_timing == "before_intervention") %>% 
    group_by(vedidk, ind_topics) %>%
    sample_n(1) %>%
    ungroup() %>%
    summarise(mean_value = mean(ind_topics, na.rm = TRUE)) %>%
    pull(mean_value)

ind_top_mean_after <- d %>% 
    filter(independence_timing == "after_intervention") %>% 
    group_by(vedidk, ind_topics) %>%
    sample_n(1) %>%
    ungroup() %>%
    summarise(mean_value = mean(ind_topics, na.rm = TRUE)) %>%
    pull(mean_value)

From the violin plot it seems that the cognitive part of the indicator has lower variability than full indicator, and the differences between treatment and (unfunded) control groups are not significant.

This might suggest that while funding helps early career researchers to become more independent from their PhD advisors overall, this is likely driven creating new collaboration networks, rather than "opening up new lines of research". That being said, the average level of cognitive (topical) independence is around `r ind_top_mean_before` (which could roughly be translated as `r round(ind_top_mean_before*100, 2)` %) even before the funding intervention and rises to about `r ind_top_mean_after` (`r round(ind_top_mean_after*100, 2)` %) in the time after the intervention.

means <- aggregate(ind_topics ~ treatment + independence_timing, data = filtered_by_subclass_1, FUN = mean)

 # Calculate means and standard errors for plotting
plot_data <- filtered_by_subclass_1 %>%
  group_by(treatment, independence_timing) %>%
  summarize(
    mean_ind_topics = mean(ind_topics),
    se_ind_topics = sd(ind_topics) / sqrt(n())
  )

  geom_violin(data = filtered_by_subclass_1, 
              aes(x = treatment, y = ind_topics, fill = independence_timing), 
              scale = "width", 
              position = position_dodge(dodge_width)) +

  geom_point(data = plot_data, 
             aes(x = treatment, y = mean_ind_topics, color = independence_timing), 
             position = position_dodge(dodge_width), 
             size = 3) +

  geom_errorbar(data = plot_data, 
                aes(x = treatment, ymin = mean_ind_topics - se_ind_topics, ymax = mean_ind_topics + se_ind_topics, color = independence_timing), 
                position = position_dodge(dodge_width), 
                width = 0.2) +

  labs(title = "Violin Plot of ind_topics Scores by Treatment and Time with Mean and CI Overlayed",
       x = "Treatment Group",
       y = "ind_topics Score") +
  theme_bw()

When looking at the scores of cognitive part of independence indicator, we cannot see notable differences across fields of study, unlike it case of the whole RII.
--> SHOULD I STATISTICALLY TEST whether adding filed of study improves prediction of the id_topics? (same way as when I tested that for full RII)??

disc_data <- d %>%
     group_by(vedidk, subclass) %>%  # Assuming 'id' is your current unique identifier
     mutate(subject_id = cur_group_id()) %>%  # This creates a unique ID for each group
     ungroup()

diff_data_tp <- disc_data %>%
  select(subject_id, independence_timing, ind_topics) %>%
  spread(independence_timing, ind_topics) %>%
  mutate(ind_topics_diff = after_intervention - before_intervention) %>%
  select(subject_id, ind_topics_diff)

disc_data <- left_join(disc_data, diff_data_tp, by = "subject_id")

disc_data <-  disc_data %>% 
     filter(!is.na(ind_topics)) %>%
     group_by(vedidk, field, ind_topics) %>%
     sample_n(1) %>%
     ungroup()

means_disc_complete <- aggregate(ind_topics ~ field, data = disc_data, FUN = mean)

# Step 1: Reorder the levels of 'field'
means_disc_complete$field <- with(means_disc_complete, factor(field, levels=unique(field[order(ind_topics)])))

se_ci_data_complete <- disc_data %>%
  group_by(field) %>%
  summarise(mean_ind_topics = mean(ind_topics),
            se_ind_topics = sd(ind_topics) / sqrt(n()),
            lower_CI = mean_ind_topics - (1.96 * se_ind_topics),
            upper_CI = mean_ind_topics + (1.96 * se_ind_topics), 
            .groups = "drop")

ggplot(data = means_disc_complete, aes(x = field, y = mean_ind_topics, fill = field)) +
  geom_bar(stat = "identity", position = "dodge") +

  # Add the number of observations in the middle of the bars
  geom_text(aes(label=count, y = mean_ind_topics/2), position=position_dodge(width=0.9), vjust=0.5) +

  # Change x-axis labels and add a title
  scale_x_discrete(labels = seq_along(unique(means_disc_complete$field))) + # replace with numbers
  labs(
    x = "Field", 
    y = "Mean ind_topics",
    title = "Differences in average ind_topics across disciplines and time"
  ) +
  scale_fill_discrete(name = "Field") +
  theme_bw()

disc_data_change <- disc_data %>% filter(!is.na(ind_topics_diff)) %>% 
     group_by(vedidk, field, ind_topics_diff) %>%
     sample_n(1) %>%
     ungroup()

means_disc_change <- aggregate(ind_topics_diff ~ field, data = disc_data_change, FUN = mean)

num_disc_change <- disc_data_change %>%
  group_by(field) %>%
  summarise(count = n(), .groups = "drop")

means_disc_change <- left_join(means_disc_change, num_disc_change, by = "field")

# Step 1: Reorder the levels of 'field'
means_disc_change$field <- with(means_disc_change, factor(field, levels=unique(field[order(ind_topics_diff)])))

# Step 2: Optionally, sort the dataframe based on the reordered levels
means_disc_change <- means_disc_change %>% arrange(field)

se_ci_data_change <- disc_data_change %>%
  group_by(field) %>%
  summarise(mean_ind_topics_diff = mean(ind_topics_diff),
            se_ind_topics_diff = sd(ind_topics_diff) / sqrt(n()),
            lower_CI = mean_ind_topics_diff - (1.96 * se_ind_topics_diff),
            upper_CI = mean_ind_topics_diff + (1.96 * se_ind_topics_diff), 
            .groups = "drop")

means_disc_change <- merge(means_disc_change, se_ci_data_change, by = "field")

ggplot(data = means_disc_change, aes(x = field, y = mean_ind_topics_diff, fill = field)) +
  geom_bar(stat = "identity", position = "dodge") +

  # Add the number of observations in the middle of the bars
  geom_text(aes(label=count, y = mean_ind_topics_diff/2), position=position_dodge(width=0.9), vjust=0.5) +

  # Change x-axis labels and add a title
  scale_x_discrete(labels = seq_along(unique(means_disc_change$field))) + # replace with numbers
  labs(
    x = "Field", 
    y = "Mean ind_topics_diff",
    title = "Average change in cognitive independence across disciplines"
  ) +
  scale_fill_discrete(name = "Field") +
  theme_bw()

@@

The results of this study provide important insights into the effects of funding interventions on researcher independence. The strongest effect we found across all control group comparisons was the effect of time - over time, researchers become more independent, regardless of their access to funding or their study discipline. This effect explains around 60% of the variance in independence.

Additionally, the observed variation in independence across different disciplines underscores the importance of considering disciplinary differences, suggested by a moderate effect size. A moderate effect size for the field effect emphasizes that certain disciplines might inherently have variations in researchers' independence, perhaps due to differences in practices, methodologies, or norms specific to each discipline. Anyway, these differences remain constant across time and funding interventions, suggesting that funding has a uniform effect on the independence across disciplines.

Importantly, the significant interaction between treatment and time when comparing treatment vs unfunded control group suggests the funding has positive effect on stimulating researchers' independence. However, the effect size is only modest, explaining about 2 % of variance in independence, indicating relatively small practical relevance. Further, the insignificant interaction when comparing the treatment vs funded control group suggests that funding in this career stage has the same effect, regardless of its type or source. Interestingly, in our sample both funded groups (treatment as well as control) started with lower independence compared to unfunded control group. This might suggest that in the early career stages, being more dependent on one's PhD advisor might be  beneficial (or even required) to obtain independent funding.

Finally, when looking closer into the composition of the independence indicator, we found that that the main driver of the increase in independence was the collaboration part of the indicator - creating new collaboration networks - rather than the cognitive part - opening up new lines of research in which their PhD advisor is not active. While the level of cognitive independence is still relatively high even early on after finishing one's PhD (researchers have around 40 % of topics not shared by their PhD advisor) and increases over time, the funding does not stimulate more novelty and divergence from the portfolio of topics held by their PhD advisors.

@@

One of the main limitations of this study is that it only focuses on Czech environment - researchers growing up and spending most of their careers in the Czech Republic, only taking into account publications affiliated with Czech research institutions. Studies testing our results on samples from other countries, and possibly tracking international mobility would strengthen our conclusions.

Further research could look more into which other factors influence researcher independence (especially the cognitive part) and how strongly compared to grant funding.

@@

@@

treatment_found_pc <- round(nrow(tar_read(final_data) %>% filter(!is.na(sup_name)) %>% filter(treatment == 1) %>% distinct(vedidk))/348*100, 2)

control_found_pc <- round(nrow(tar_read(final_data) %>% filter(!is.na(sup_name)) %>% filter(treatment != 1) %>% distinct(vedidk))/nrow(tar_read(final_data) %>% filter(treatment != 1) %>% distinct(vedidk))*100, 2)

treatment_match <- left_join(tar_read(final_data) %>% filter(!is.na(sup_name)), tar_read(sup_alg), by = "vedidk") %>% 
    mutate(match = ifelse(sup_vedidk.x == sup_vedidk.y, 1, 0))

match_yes <- nrow(treatment_match %>% filter(match == 1) %>% distinct(vedidk))
match_yes_pc <- round(nrow(treatment_match %>% filter(match == 1) %>% distinct(vedidk))/nrow(treatment_match %>% distinct(vedidk))*100, 2)

match_no <- nrow(treatment_match %>% filter(match == 0) %>% distinct(vedidk))
match_no_pc <- round(nrow(treatment_match %>% filter(match == 0) %>% distinct(vedidk))/nrow(treatment_match %>% distinct(vedidk))*100, 2)

match_na <- nrow(treatment_match %>% filter(is.na(match)) %>% distinct(vedidk))
match_na_pc <- round(nrow(treatment_match %>% filter(is.na(match)) %>% distinct(vedidk))/nrow(treatment_match %>% distinct(vedidk))*100, 2)

Data about PhD student-PhD advisor connections are usually not available. One must search for these connections manually on the internet, which is time consuming and not fully reliable (we were only able to find about `r treatment_found_pc` % of these connections in our treatment group and `r control_found_pc`) % in control groups. Therefore, we tried to come up with an alternative way of identifying supervisors from the available data: we assumed that since many researchers only start their publication career during their PhD studies, their PhD supervisors might often coauthor their first publications. That led us to creating an algorithm to identify the supervisor solely from the student's publication history as "the most frequent co-author of the first 5 publications".

To check whether we can use "the most frequent co-author of the first 5 publications" as a proxy to identify supervisors, we have compared the supervisors identified via this method with the manually found supervisors for each researcher in our sample. Across our full sample of `r nrow(tar_read(final_data) %>% filter(!is.na(sup_name)) %>% distinct(vedidk))` researchers for whom we identified supervisors manually, `r match_yes` (`r match_yes_pc` %) had their most frequent co-author same as their supervisor and `r match_no` (`r match_no_pc` %) had someone other than their supervisor as their most frequent co-author in their first 5 publications, and `r match_na` (`r match_na_pc`%) had no co-author in their first 5 publications.

---------> should I put the next paragraph here? If yes, I should ask Luzar whether I can publish it, show the data to reviewers and ask him how to cite him. (the code is at the bottom of the fuction sup_test.R)

@@

This suggest that the algorithmic approach as we defined is not able to identify real supervisors often enough. Either new algorithm is needed or future studies should redefine the "supervisory role" based on other characteristics than formal supervision.
